### 2014-04-14 paper/exampleobjects.tex
roboto images

\begin{figure}[t]
\centering
    \includegraphics[width=3.4in]{figures/sign.png}
\caption{A two-state animated neon sign designed using our tool.  (a) shows the input SVG files, with the eyes (non-animated) in black and the two states of the mouth in {\color{blue}blue} and {\color{gray}gray}.  (b) shows the resultant mesh when we subtracted the generated tubes, with rear exit tubes circled in {\color{blue}blue} \valkyrie{fix this with boolean magic}. In (c), we show the fabricated sign.}
\label{fig:neon}
\end{figure}

@@

The pipes are threaded with electroluminescent wire which is lit in sequence, using an EL wire sequencer, to create the animation.

>>>>

\begin{figure}[t]
\centering
    \includegraphics[width=3.4in]{figures/sign.png}
\caption{A two-state animated neon sign designed using our tool.  (a) shows the input SVG files, with the eyes (non-animated) in black and the two states of the mouth in {\color{blue}blue} and {\color{gray}gray}.  (b) shows the tubes we subtracted from the mesh, rear exit tubes circled in {\color{blue}blue}. In (c), we show the fabricated sign.}
\label{fig:neon}
\end{figure}

@@

The pipes are threaded with electroluminescent wire which is lit in sequence, using an sequencer, to create the animation.
